\Huge Conferences and Cost of Carbon

### 2019-06-03 main.tex
Added distribution of participants' origin

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs.png}
\caption{Carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi} 
\label{fig:confs}
\end{figure}

@@

Ultimately, responding to the inevitability of expensive carbon may involve
rethinking the whole basis of how academic computer science is done.
\bcp{
\begin{itemize}
\iten Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.
\item monitoring and mitigating carbon costs should be an ACM-level activity
\end{itemize}
}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=6in]{SIGPLAN-confs.png}
\includegraphics[width=6in]{ParticipantsOriginAll.png}
\caption{Top: carbon footprint per participant for travel to recent SIGPLAN
  conferences\iflater\bcp{Get better file from the other paper, or get
    better version of this one from Crista.}\fi Bottom: origin of participants for each conference.} 
\label{fig:confs}
\end{figure}

@@

Ultimately, responding to the inevitability of expensive carbon may involve
rethinking the whole basis of how academic computer science is done.
\bcp{
\begin{itemize}
\item Add a bit of meat about how the current economic model may be
  unsustainable and reworking it will involve substantial organizational
  changes.
\item monitoring and mitigating carbon costs should be an ACM-level activity
\end{itemize}
}
